\documentclass[12pt]{article}

\usepackage[margin=1cm, paperheight=28in]{geometry}
\usepackage{amsfonts, multicol, cancel, amsxtra}

\title{Probabily Homework}
\author{Michael Padilla}

\begin{document} 
\maketitle
\section*{Exercises for Section 5.1}
\begin{enumerate}
    \item A card is randomly selected from a deck of 52 cards. What is the chance that the card is red or a king?\\
	$|S| = 52$ , red = 26, kings = 4, $|E| = 28$\\
	$P(E) = \dfrac{28}{52}$
    \item[5] Toss a dice 5 times in a row. What is the probability that you will get the same number on each roll?\\
	$|S| = 6x6x6x6x6 = 6^5$, $|E| = \{all1, all2, all3, all4, all5, all6\} = 6$
	$p(E) = \dfrac{6}{6^5}$
    \item[7] You have a pair of dice, a white one and a black one. Toss them both. What is the probability that they show the same number?\\
	$|S| = 6x6, |E| = \{11,22,33,44,55,66\} = 6$\\
	$p(E) = \dfrac{6}{6x6}$
    \item[11] Toss a coin 8 times. Find the probability that the first and last tosses are heads.\\
	$|S| = 2^8, |E| = 1x2x2x2x2x2x2x1 = 1^2x2^6$\\
	$P(E) = \dfrac{2^6}{2^8}$
    \item[13] Five cards are dealt from a shuffled 52-card deck. What is the probability of getting three red cards and two clubs?\\
	$|S| = C_{52}^5, |E| = C_{26}^3 x C_{13}^2$\\
	$P(E) = \dfrac{C_{26}^3 x C_{13}^2}{C_{52}^5}$
    \item[15] Alice and Bob each randomly pick an integer from 0 to 9.
	$|S| = 10x10$
	\begin{itemize}
	    \item What is the probability that they pick the same number?\\
		$|E| = 10, P(E) = \dfrac{10}{10x10}$
	    \item What is the probability that they pick different numbers?\\
		$|E^c| = 100-10=90, P(E^c) = \dfrac{90}{10x10}$
	\end{itemize}
\end{enumerate}
\section*{Exercises for Section 5.2}
\begin{enumerate}
    \item A card is taken off the top of a shuffled 52-card deck. What is the probability that it is black or an ace?\\
	$|S| = 52, p(black) = \dfrac{26}{52}, p(ace)=\dfrac{4}{52}, p(A\cap B) = \dfrac{2}{52}$\\
	$p(A\cup B) =  4/52 + 26/52 - 2/52 = \dfrac{28}{52}$
    \item [3] What is the probability that a 5-card hand dealt off a shuffled 52-card deck contains at least one red card?\\
	$|S| = C_{52}^5, |E| = C_{26}^{5}, p(E^c) = 1 - \dfrac{C_{26}^5}{C_{52}^5}$
    \item [7] Two cards are dealt off a shuffled 52-card deck.What is the probability that the cards are both red or both aces?\\
	$|S| = C_{52}^2, |A|=C_{26}^2, |B|=C_{4}^2, |A\cap B| = 1$\\
	$p(A\cup B) = \dfrac{C_4^2}{C_{52}^2} + \dfrac{C_{26}^2}{C_{52}^2} - \dfrac{1}{C_{52}^2}$
    \item [11] A dice is rolled 5 times. Find the probability that not all of the tosses are even.\\
	$|S| = 6^5, |E| = 3^5, |E^c| = 5^5 - 3^5$\\
	$p(E^c) = \dfrac{6^5-3^5}{6^5}$
    \item [17] In a shuffled 52-card deck, what is the probability that neither the top nor bottom card is a heart?\\
	$|S| = 52x51, |E| = 39x38$\\
	$p(E)= \dfrac{39x38}{52x51}$
\end{enumerate}
\section*{Exercises for Section 5.3}
\begin{enumerate}
    \item [2] A box contains six tickets: A A B B B E . You remove two tickets, one after the other. What is the probability that both tickets are vowels?\\
	$|S| = 6x5, |E| = 3x2, p(E) = \dfrac{3x2}{6x5}$
    \item [4] A card is drawn off a 52-card deck. Let A be the event “The card is a heart.” Let B be the event “The card is a queen.” Are these two events independent or dependent?\\
	$|S| = 52, p(A) = 13/52 = 1/4, p(B) = 4/52 1/13, p(A|B) = 1/4, p(B|A) = 1/13$\\
	\textbf{They're independent}
    \item [7] Say A and B are events with $P(A) = 2/3, P(A|B) = 3/4$, and $P(B|A) = 1/2$. Find $p(B)$.\\
	$p(A)\cdot p(B|A) = p(A\cap B) = p(B) \cdot p(A|B)$\\
	$2/3 \cdot 1/2 = p(B) \cdot 1/4$\\
	$p(B) = \dfrac{4}{9}$
    \item [9] A box contains 2 red balls, 3 black balls, and 4 white balls. One is removed, and then another is removed. What is the probability that no black balls were drawn?\\
	$|S| = 9x8, |E| = 6x5, p(E) = \dfrac{6x5}{9x8}$
    \item [11] A coin is flipped 5 times, and there are more tails than heads. What is the probability that the first flip was a tail?\\
	$|S| = 2^5 = 32, A = more\ tails, B = first\ tail, p(B|A) = p(A\cap B)/p(A)$\\
	$|A \cap B| = C_4^2 + C_4^3 + C_4^4 = 11, |A| = C_5^3 + C_5^4 + C_5^5 = 16$\\
	$p(B|A) = \dfrac{11}{16}$
\end{enumerate}
\section*{Exercises for Section 5.5}
\begin{enumerate}
    \item At a certain college, 40\% of the students are male, and 60\% are female. Also, 20\% of the males are smokers, and 10\% of the females are smokers. A student is chosen at random. If the student is a smoker, what is the probability that the student is female?\\
	S1 = male, S2 = female, $p(s2|E) = p(s2) \cdot p(e|s2)/p(s2) \cdot p(e|s2) + p(s1) \cdot p(e|s1)$\\
	$p(s2|E) = \dfrac{0.6 \cdot 0.10}{0.6 \cdot 0.10 + 0.4 \cdot 0.2}$
    \item At a certain college, 30\% of the students are freshmen. Also, 80\% of the freshmen live on campus, while only 60\% of the non-freshman students live on campus. A student is chosen at random. If the student lives on campus, what is the probability that the student is a freshman?\\
	S1 = non-freshman, S2 = freshmen, $p(s2|E) = p(s2) \cdot p(e|s2)/p(s2) \cdot p(e|s2) + p(s1) \cdot p(e|s1)$\\
	$p(s2|E) = \dfrac{0.3 \cdot 0.8}{0.3 \cdot 0.8 + 0.7 \cdot 0.6}$
    \item A jar contains 4 red balls and 5 white balls. A random ball is removed, and then another is removed. If the second ball was red, what is the probability that the first ball was red?\\
	$|S| = 9x8$, A = 1st is red, B = 2nd is red\\
	$p(A|B) = \dfrac{3x4}{8x4} = 3/8$
\end{enumerate}
\end{document}
