\documentclass[12pt]{article}

\usepackage[margin=1cm, paperheight=44in]{geometry}
\usepackage{amsfonts, multicol, pgfplots, tikz, cancel}

\pgfplotsset{compat=1.18}
\title{Counting Homework}
\author{Michael Padilla}

\begin{document} 
\maketitle
\section*{Exercises for Section 4.2}
\begin{enumerate}
    \item Consider lists made from the letters T, H, E, O, R, Y, with repetition allowed.
	\begin{itemize}
	    \item Length 4 lists: \textbf{6x6x6x6}
	    \item Length 4 lists that begin with T: \textbf{1x6x6x6}
	    \item Length 4 lists that do not begin with T: \textbf{5x6x6x6}
	\end{itemize}
    \item [3] How many lists of length 3 can be made from the symbols A, B, C, D, E, F if...
	\begin{itemize}
	    \item repetition is allowed: \textbf{6x6x6}
	    \item repetition is not allowed: \textbf{6x5x4}
	    \item repetition is not allowed and the list must contain the letter A:\\
		(A,\_,\_) = 1x5x4\\
		(\_,A,\_) = 5x1x4\\
		(\_,\_,A) = 5x4x1\\
		\textbf{= 3(5x4)}
	    \item repetition is allowed and the list must contain the letter A:\\
		$|U| = 6x6x6, |X^c| = 5x5x5, |X| = (6x6x6)-(5x5x5)$
	\end{itemize}
    \item [5] This problem involves 8-digit binary strings such as 10011011 or 00001010 (i.e.,
8-digit numbers composed of 0’s and 1’s).
	\begin{itemize}
	    \item How many such string are there? \textbf{2x2x2x2x2x2x2x2}
	    \item How many such string end in 0? \textbf{2x2x2x2x2x2x2x1}
	    \item How many such string have 1's for their second and fourth digits? \textbf{2x1x2x1x2x2x2x2}
	    \item How many such string have 1's for their second or fourth digits?\\
		$|A\cup B| = 2x1x2x1x2x2x2x2$\\
		$|A| = 2x1x2x2x2x2x2x2$\\
		$|B| = 2x2x2x1x2x2x2x2$\\
		$= 2^7 + 2^7 - 2^6 = 192$
	\end{itemize}
    \item [7] This problem concerns 4-letter codes made from the letters A, B, C, D, ... , Z.
	\begin{itemize}
	    \item How many such codes can be made? \textbf{26x26x26x26}
	    \item How many such codes have no two consecutive letters the same?\\
		letter 1: any of all 26\\
		letter 2: 26 - the first = 25\\
		letter 3: 26 - the second = 25\\
		letter 4: 26 - the third = 25\\
		\textbf{26x25x25x25}
	\end{itemize}
    \item [9] A new car comes in a choice of five colors, three engine sizes and two transmissions. How many different combinations are there?\\
	Total length is 3, first is 5 colors, second is 3 engine sizes and last is 2 transmissions.\\
	\textbf{5x3x2}
    \item [10] A dice is tossed four times in a row. There are many possible outcomes. How many different outcomes are possible?\\
	Length is 4, a dice has numbers from 1 to 6. \textbf{6x6x6x6}
\end{enumerate}
\section*{Exercises for Section 4.3}
\begin{enumerate}
    \item Five cards are dealt off of a standard 52-card deck and lined up in a row.
	\begin{itemize}
		\item How many such lineups are there that have at least one red card?\\
		    $|U| = $52x51x50x49x48, $|X^c|$ = 26x25x24x23x22\\
		    \textbf{(52x51x50x49x48) - (26x25x24x23x22)}
		\item How many such lineups are there in which the cards are either all black or all hearts?\\
		    They are not black cards that are hearts, so we use the addition principle:\\
		    All black cards: 26x25x24x23x22\\
		    All hearts: 13x12x11x10x9\\
		    \textbf{(26x25x24x23x22) + (13x12x11x10x9)}
	\end{itemize}
    \item [3] Five cards are dealt off of a standard 52-card deck and lined up in a row.
	\begin{itemize}
		\item How many such lineups are there in which all 5 cards are of the same color (i.e., all black or all red)?\\
		    There can't be black cards that are red, so we use addition principle:\\
		    All black cards: 26x25x24x23x22\\
		    All red cards: 26x25x24x23x22\\
		    \textbf{(26x25x24x23x22) + (26x25x24x23x22)}
	\end{itemize}
    \item [5] How many integers between 1 and 9999 have no repeated digits?\\
	1-digit: 9, 2-digit: 9x9, 3-digit: 9x9x8, 4-digit: 9x9x8x7\\
	\textbf{9+(9x9)+(9x9x8)+(9x9x8x7)}
	\begin{itemize}
		\item How many have at least one repeated digit?\\
		    Using the substraction principle:\\
		    $|U| = 9999, |x^c| =$ 9+(9x9)+(9x9x8)+(9x9x8x7)\\
		    $|X|$ = \textbf{9999 -(9+(9x9)+(9x9x8)+(9x9x8x7))}
	\end{itemize}
    \item [7] A password on a certain site must be five characters long, made from letters of the alphabet, and have at least one upper case letter.
	\begin{itemize}
	    \item How many different passwords are there?\\
		$|U| = 52^5, |X^c= 26^5|$\\
		$|X| = $\textbf{$52^5 - 26^5$}
	    \item What if there must be a mix of upper and lower case?\\
		$|U| = 52^5, |X^c= 26^5 \cdot 2|$\\
		$|X| = $\textbf{$52^5 - (26^5 + 26^5)$}
	\end{itemize}
\end{enumerate}
\section*{Exercises for Section 4.4}
\begin{enumerate}
    \item [3] How many 5-digit positive integers are there in which there are no repeated
digits and all digits are odd?\\
	Odds: 1,3,5,7,9, total 5 numbers. \textbf{=5!}
    \item [5] Using only pencil and paper, find the value of $\frac{120!}{118!}$\\
	$\frac{120\cdot 119 \cdot \cancel{118!}}{\cancel{118!}} = 120\cdot 119$
    \item [9] How many permutations of the letters A, B, C, D, E, F, G are there in which the
three letters ABC appear consecutively, in alphabetical order?\\
	n = 7 - ABC = 5, \textbf{5!}
    \item [13] How many lists of length six (with no repetition) can be made from the 26 letters
of the English alphabet?\\
	$P(26,6) =$ \textbf{26x25x24x23x22x21}
    \item [15] In a club of 15 people, we need to choose a president, vice-president, secretary,
and treasurer. In how many ways can this be done?\\
	$P(15, 4) =$ \textbf{15x14x13x12}
    \item [17] Three people in a group of ten line up at a ticket counter to buy tickets. How
many lineups are possible?\\
	$P(10, 3) =$ \textbf{10x9x8}
\end{enumerate}
\section*{Exercises for Section 4.5}
\begin{enumerate}
    \item [5] How many 16-digit binary strings contain exactly seven 1’s? (Examples of such
strings include 0111000011110000 and 0011001100110010, etc.)\\
	$C_{16}^7 = \frac{16!}{7!9!}$
    \item [6] $|{X \in P({0,1,2,3,4,5,6,7,8,9}): |X| = 4}|$\\
	$= C_{10}^4 = \frac{10!}{4!6!}$
    \item [7] $|{X \in P({0,1,2,3,4,5,6,7,8,9}): |X| < 4}|$\\
	We can have a $\phi$ subset. Therefore $= C_{10}^0 + C_{10}^1 + C_{10}^2 + C_{10}^3$
    \item [17] How many 10-digit binary strings are there that have exactly four 1’s or exactly
five 1’s?\\
	$C_{10}^4 + C_{10}^5$
	\begin{itemize}
	    \item How many do not have exactly four 1’s or exactly five 1’s?\\
		$|U| = 2^{10}$\\
		$2^{10} - C_{10}^4 - C_{10}^5$
	\end{itemize}
    \item [19] A 5-card poker hand is called a flush if all cards are the same suit. How many
different flushes are there?\\
	There are 13 cards in each suit and there are 4 suits. There are $C_{13}^5 \cdot 4$ different flushes.
\end{enumerate}
\section*{Exercises for Section 4.7}
\begin{enumerate}
    \item At a certain university 523 of the seniors are history majors or math majors (or both). There are 100 senior math majors, and 33 seniors are majoring in both history and math. How many seniors are majoring in history?\\
	$|A\cup B| = 523, |A|(math) = 100, |B|(history) = ?, |A\cap B|(both) = 33$\\
	$523 = 100 + |B| - 33$\\
	$523-100+33=|B|$\\
	$|B| = 456$
    \item [3] How many 4-digit positive integers are there that are even or contain no 0’s?\\
	$|A \cup B| = ?, |A|(even) = 9x10x10x5, |B|(no\ 0s) = 9x9x9x9, |A\cap B|(both) = 9x9x9x4$\\
	$|A\cup B| = (9x10x10x5) + (9x9x9x9) - (9x9x9x4)$
    \item [13] How many 8-digit binary strings end in 1 or have exactly four 1’s?\\
	$|A\cup B| = ?, |A|(end\ 1) = 2x2x2x2x2x2x2x1, |B|(four\ 1s)=C_{8}^4, |A\cap B| = 1\cdot C_7^3$\\
	$|A\cup B| = (2x2x2x2x2x2x2x1) + (C_8^4) - (C_7^3)$ 
    \item [15] How many 10-digit binary strings begin in 1 or end in 1?
	$|A \cup B| = ?, |A|(beging \ 1) = 1\cdot 2^9, |B|(end\ 1) = 2^9 \cdot 1, |A\cap B|(both) = 1\cdot 2^8 \cdot 1$\\
	$|A\cup B| = 2^9 + 2^9 - 2^8$
\end{enumerate}
\section*{Exercises for Section 4.8}
\begin{enumerate}
    \item ffff
    \item [7] ffff
    \item [9] ffff
    \item [11] ffff
    \item [20] ffff
\end{enumerate}
\end{document}
